\documentclass[letterpaper,11pt]{article}

\usepackage{geometry}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{hyperref}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------


\begin{document}

\begin{center}
    \textbf{\huge \scshape Kabir Samsi} \\ \vspace{1pt}
    { \small
        \href{https://kabirsamsi.com}{\underline{kabirsamsi.com}} $|$ \href{mailto:samsikabir@gmail.com}{\underline{samsikabir@gmail.com}} $|$ 
        \href{https://linkedin.com/in/kabir-samsi}{\underline{linkedin.com/in/kabir-samsi/}} $|$ \href{https://github.com/KabirSamsi}{\underline{github.com/KabirSamsi}}
    }
\end{center}

{\small Software engineer \& researcher passionate and highly skilled in software design, compiler engineering, programming language theory/research \& full-stack development. Passionate about engineering, research, team leadership \& teaching.\\[-10pt]}
    
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cornell University}{Ithaca, NY}
      {Bachelor of Arts – Computer Science, Mathematics \& Music} {May 2026}
      \resumeItemListStart
        \resumeItem{\textbf{Graduate Coursework}: Compilers, Programming Languages, Software Systems}
        \resumeItem{\textbf{Relevant Undergraduate Coursework:} Algorithms, Data Structures \& OOP (Honors), Machine Learning, Functional Programming, Operating Systems, Databases, Abstract Algebra, Linear Algebra, Probability Theory}
        \resumeItem{\textbf{GPA 3.8/4.0, Dean's List} (All Semesters), \textbf{CS Honors Track} (Focus in Programming Languages/Compilers)\\[-2pt]}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lead Undergraduate Researcher}{June 2024 -- Present}
      {\href{https://capra.cs.cornell.edu/}{Capra Research Group} @ Cornell University}{Ithaca, NY}
      \resumeItemListStart
        \resumeItem{Researching programming language design for packet scheduling \& optimizations in software-defined networking.}
        \resumeItem{Developing the Rio language, compiler \& arbiter for compiling packet scheduling policies onto hardware.}
        \resumeItem{Led the design, formalization \& hardware representations of the PIEO and PIEO Tree data structures.}
        \resumeItem{Developed a type system, typechecker and formally verified operational semantics for the language.}
        \resumeItem{Coauthoring a publication on formalisms, semantics \& hardware abstractions in programmable packet scheduling.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Head Teaching Assistant}{August 2023 -- Present}
      {CS3110 (Data Structures \& Functional Programming) @ Cornell University}{Ithaca, NY}
      \resumeItemListStart
        \resumeItem{Taught functional programming, data structures, interpreter design \& formal verification to thousands of students.}
        \resumeItem{Led the course's lab material development \& organization; hosted weekly discussion sections \& office hours.}
        \resumeItem{Inagurated and led hosting of the course's pre-exam recitation program; created 200+ slides of recitation material.}
        \resumeItem{Trained 60+ TAs over multiple semesters in lab management and discussion teaching.}
        \resumeItem{Two-time recipient of Cornell's Outstanding Computing \& Information Science Teaching Assistant Award.}
        \resumeItemListEnd
        
    \resumeSubheading
      {Senior Software Engineer}{August 2023 -- Present}
    {\href{https://www.cs.cornell.edu/projects/cms/cmsx/}{CMSX} @ Cornell University}{Ithaca, NY}
      \resumeItemListStart
        \resumeItem{Full-stack developer for Cornell CIS's primary course management platform (8K+ users and 100+ courses).}
        \resumeItem{Team's expert and supervisor on the structure, development \& maintenance of the platform's JSP frontend.}
        \resumeItem{Developing a staff-side model for securely serializing, importing \& exporting course templates in XML \& JSON.}
        \resumeItem{Led a subteam of developers in designing an optimized regrade system and secure enrollment.}
        \resumeItem{Implemented parsing, verification and new integrations for staff-side, grading-related CSV uploads.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Engineer}{October 2022 -- May 2024}
      {Cornell Lab of Ornithology}{Ithaca, NY}
      \resumeItemListStart
        \resumeItem{Classified 5000+ images and developed audiovisual bird ID models \& data cleaning scripts for the \href{https://merlin.allaboutbirds.org/}{Merlin Project}.}
        \resumeItem{Curated database profiles for 300+ species splits for the \href{https://ebird.org/about}{EBird} packs throughout Eastern \& Southeast Asia.\\[-5pt]}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Franz} $|$ \emph{Rust}}{March 2024 -- Present}
          \resumeItemListStart
            \resumeItem{A domain-specific programming language \& compiler targeted towards compact and modular musical composition, using a medium of text-based musical notation. Compiles to ChucK, an audio representation language.\\[-2pt]}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Saberchat (Team Lead)} $|$ \emph{MEAN/MERN}}{June 2020 -- May 2022}
          \resumeItemListStart
            \resumeItem{Led the development of a community platform infrastructure used by schools \& organizations. Includes content-sharing systems, an online tutoring center \& a streamlined preorder/inventory interface for retail groups.\\[-1pt]}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{FindYourBird (Founder \& Lead)} $|$ \emph{MEAN/MERN}}{June 2020 -- May 2024}
          \resumeItemListStart
            \resumeItem{Founded and built a bird ID, info \& observation logging platform used by amateur ornithologists. Includes a search \& identification system, information pages on 200+ different species \& user-specific target species and locations.\\[-2pt]}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Rust, TypeScript, JavaScript, Python, OCaml, C, C++, Swift, Haskell, Ruby, Go, HTML, CSS} \\
     \textbf{Frameworks}{: Express.js, Node.js, React.js, NextJS, Ajax, LLVM, Coq, Flask, Pandas, TensorFlow, PyTorch} \\
     \textbf{Databases \& Systems}{: MongoDB, SQL/PostgreSQL/MariaDB, Neo4j, Linux, Git, Docker, AWS}\\
     \textbf{Expertise}{: Software Engineering, Compiler Design, Programming Languages, Research, ML, Fullstack Development} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
